%        File: cv.tex
%     Created: Mon Dec 08 08:00 PM 2014 C
% Last Change: Mon Dec 08 08:00 PM 2014 C
%
\documentclass[11pt,a4paper]{resume}

\begin{document}

\name{Guohua Wu}
\address{+86 185-0137-0591}
{ghmeta@163.com}
{Room 1332, Student Apartment 10, BUPT,  No. 10 Xi Tu Cheng Road,  Beijing, 100876, China}

\section{Education}
\noindent\begin{tabularx}{\textwidth}{@{}p{14em}p{8.5em}p{3em}p{7em}R@{}}
\textbf{Beijing University of Posts and Telecommunications} & Computer Science and Technology & M.S.E & GPA:\@ 87.73/100 (Rank: 4/400) & Sept. 2013\timedash{}Expected Mar. 2016\\[0.3em]
\textbf{Beijing University of Posts and Telecommunications} & Intelligence Science and Technology& B.E & GPA:\@ 89.64/100 (Rank: 1/32) & Sept. 2009\timedash{}Jun. 2013
\end{tabularx}
\vspace{-1.7em}
%\education{Beijing University of Posts and Telecommunications, School of Computer Science}
%{Beijing, China}
%{Master of Science in Engineering, Computer Science and Technology}
%{Sept. 2013\timedash{}Expected Mar. 2016}
%{GPA:\@ 87.73/100~(ranked $4^{th}$ out of over 400 students)}

%\education{Beijing University of Posts and Telecommunications, School of Computer Science}
%{Beijing, China}
%{Bachelor of Engineering, Intelligence Science and Technology}
%{Sept. 2009\timedash{}Jun. 2013}
%{GPA:\@ 89.64/100~(ranked $1^{st}$ in major)}

\section{Technical Skills}
%\begin{itemize}[leftmargin=*,nosep,labelsep=0mm,label={}]
  %\item \textbf{Languages:}
  %\begin{itemize}[leftmargin=*,labelindent=\parindent,nosep,label={}]
    %\begin{tabular}{@{}p{125pt}l} % two cloumns, first width is 10em, and left margin is 0pt
    %Most experienced with:     &     Python, C, C\verb|++| and Java \\
    %\end{tabular}
  %\end{itemize}
%\end{itemize}
\begin{skilltable}
\textbf{Languages:}     &     Python, C, C\verb|++| and Java \\
\textbf{Research Fields:}     &     Natural Language Processing, Dialogue Management and Machine Learning\\
\textbf{Software:}     &    Linux, Vim, Awk, Sed, Latex, Intellij Idea, Eclipse, Git and MySQL
\end{skilltable}

\section{Intenship Experience}
\internship{Alibaba Group, Alimama Display Advertising}{Algorithm Engineer Intern}{May 2015\timedash{}Sept. 2015}
\begin{workitemize}
  \item Implemented advertiser-based collaborative filtering algorithm to
    generate black-box crowd packages for advertisers.
  %\item Increased CTR of alchemy targeting by 24\% through implementing a page
    %view filter.
  \item Developed a tool to evaluate offline the performance of advertising on
    black-box crowd packages.
  \item Maked frequently-used Ad performance reports generation process 30
    times faster by developing a middle table.
  %\item Reduced frequently-used Ad performance reports generation time from 30 min to 1
    %min by developing a middle table.
  \item Developed targeting performance reports of various dimensions for
    targeting performance monitor.
\end{workitemize}

\internship{Nuance}{Natural Language Processing Engineer Intern}{Mar. 2014\timedash{}Jul. 2014}
\begin{workitemize}
  \item Developed a Natural Language Understanding~(NLU) module for in-car
    voice assistant.
  \item Generated spoken utterances for 12 domains by filling dictionary into
    corresponding templates' slots, and extracted features from these utterances
    to produce training data for Maxent classifier and CRF-based slot extractor.
  \item Developed a Rule-based NLU for domains whose spoken utterances are
    relatively limited.
\end{workitemize}

\internship{Baidu, Wenku}{Software Development Engineer in Test Intern}{Dec. 2012\timedash{}Apr. 2013}
\begin{workitemize}
  \item Tested back-end interfaces for Wenku~(wenku.baidu.com) through
    automating test.
  \item Created test cases from the functional requirements, reported bug and
    wrote test report.
  %\item Developed bash script to build test environment automatically.
\end{workitemize}

\section{Projects}
\project{SIGHAN Chinese Word Segmentation~(Team Size: 2)}{Core Developer}{May 2014\timedash{}Aug. 2014}
\begin{workitemize}
  \item Presented a CRF-based Chinese segmentation system integrating
    supervised, unsupervised~(Accessor Variety) and lexical features, and
    refined segmentation result with new word detection.
  \item Completed segmentation system development and feature extraction, and
    \emph{improved 2\%} performance~(F1 score) by integrating unsupervised and
    lexical features.
  \item \emph{Our system ranked first in the 3rd CIPS-SIGHAN bakeoff with
    precision 0.968, recall 0.978 and F1 score 0.972.}
\end{workitemize}

\project{POMDP-based Spoken Dialog System~(Team Size: 1)}{Core Developer}{Sept. 2014\timedash{}Present}
\begin{workitemize}
  \item Implemented a web-based spoken dialog system, and casted spoken dialog
    system as a Partially observable Markov decision process~(POMDP). Estimated
    POMDP's parameters from dialog corpus and solved POMDP to generate policy.
    Consequently, interacted with user according to POMDP's policy instead of
    manual rules.
  \item Implemented POMDP-based dialogue management module and natural language
    understanding module based on Maximum Entropy and CRF.\@
  %\item Called Google Speech API to implemented automatic speech recognition
    and speech synthesis.
\end{workitemize}

\project{Samsung Chinese Material Crawling~(Team Size: 3)}{Core Developer}{Sept. 2013\timedash{}Dec. 2013}
\begin{workitemize}
  \item Implemented a web crawler supporting main textual content extracting
    and duplicate paragraph removal.
\end{workitemize}

\project{Dialogue System in Given Field~(Team Size: 3)}{Core Developer}{Mar. 2012\timedash{}Jul. 2012}
\begin{workitemize}
  \item Provided Android LBS applications to recommend restaurants through
    human-machine conversation.
  \item Extracted restaurants' information, designed information retrieval
    interfaces and implemented Android application.
  \item \emph{Awarded the Second Prize of the Chinese University Students
    Intelligence Design Contest, 2012.}
\end{workitemize}

\section{Awards}
\scholarship{Vmware Enterprise Scholarship}{ranked $4^{th}$ out of over 400 students}{Sept. 2013\timedash{}Sept. 2014}
\scholarship{Changfei Enterprise Scholarship}{ranked $1^{st}$ in major}{Sept. 2011\timedash{}Sept. 2012}
\scholarship{National Scholarship for Encouragement}{ranked $1^{st}$ in major}{Sept. 2010\timedash{}Sept. 2011}
\scholarship{National Scholarship}{ranked $1^{st}$ in major}{Sept. 2009\timedash{}Sept. 2010}
\award{First prize in BUPT's Innovation Award Contest}{Jun. 2012}
\award{Second prize in Beijing Undergraduate Electronic Design Contest}{Jun. 2012}

\end{document}


